Considering scale in multilayer animal social networks

### 2020-06-16 paper/manuscript.Rmd
minor edits in discussion

Monolayer network approaches have been increasingly used to link social network
position with individual fitness, including in primates [@Brent_2017;
@Thompson_2019], dolphins [@Stanton_2012; @Stanton_2011], and birds
[@McDonald_2007; @Royle_2012]. Social scale has emerged as an important variable
for understanding fitness consequences in the context of social network
positions <!-- TODO JWT check --> [@Almeling_2016; @Berger_2015; @Brent_2017;
@Holekamp_2011]. Defining the social scale at which to generate networks is an
essential consideration for social network analysis <!-- with direct impacts on
outcomes blah-->[@Castles_2014; @Carter_2015; @Farine_2015a]. Proximity-based
social networks generated using GPS location data require using a social scale,
specifically a spatial distance threshold, to define social associations. We
found increasing individual graph strength across three habitat layers with
increasing spatial distance threshold (Figure \@ref(fig:socres)). In addition,
habitat layers differed in their response to spatial distance threshold, with
open and forage with a larger increase in graph strength and greater variation
across individuals. These results emphasize that multilayer network metrics are
directly influenced by social scale, in this case the spatial distance
threshold.

@@

The emergent relationship between habitat and sociality has been explored by the
distribution and phenology of resources and use of social information. For
example, cougar (*Puma concolor*) home ranges overlapped more in regions with
high hunting opportunity, a proxy for resource richness [@Elbroch_2015]. Caribou
(*Rangifer tarandus*) sociality differed between seasons, where social
associations were stronger in winter and contrastingly low in summer when
resource availability are more homogeneous [@Peignier_2019]. Bison (*Bison
bison*) showed stronger habitat selection in larger groups and avoidance of
predation risk was a main factor contributing to their habitat selection
[@Fortin_2009]. These examples, comparing sociality and habitat selection across
temporal or spatial contexts, are implicitly multilayer analyses.

>>>>

Monolayer network approaches have been increasingly used to link social network
position with individual fitness, including in primates [@Brent_2017;
@Thompson_2019], dolphins [@Stanton_2012; @Stanton_2011], and birds
[@McDonald_2007; @Royle_2012]. Social scale has emerged as an important variable
for understanding fitness consequences in the context of social network
positions <!-- TODO JWT check --> [@Almeling_2016; @Berger_2015; @Brent_2017;
@Holekamp_2011]. Defining the social scale to generate networks is an
essential consideration for social network analysis <!-- with direct impacts on
outcomes blah-->[@Castles_2014; @Carter_2015; @Farine_2015a]. Proximity-based
social networks generated using GPS location data require using a social scale,
specifically a spatial distance threshold, to define social associations. We
found increasing individual graph strength across three habitat types with
increasing spatial distance threshold (Figure \@ref(fig:socres)). In addition,
habitat layers differed in their response to spatial distance threshold, with
open and forage with a larger increase in graph strength and greater variation
across individuals. These results emphasize that multilayer network metrics are
directly influenced by social scale, in this case the spatial distance
threshold.

@@

The emergent relationship between habitat and sociality has been explored by the
distribution and phenology of resources and use of social information. For
example, cougar (*Puma concolor*) home ranges overlapped more in regions with
high hunting opportunity, a proxy for resource richness [@Elbroch_2015]. Caribou
(*Rangifer tarandus*) social network graph strength differed between seasons, where 
graph strength was stronger in winter and contrastingly low in summer when
resource availability are more homogeneous [@Peignier_2019]. Bison (*Bison
bison*) showed stronger habitat selection in larger groups and avoidance of
predation risk was a main factor contributing to their habitat selection
[@Fortin_2009]. These examples, comparing sociality and habitat selection across
temporal or spatial contexts, are implicitly multilayer analyses.
